Taxonomic bias can create spurious results in microbiome differential-abundance analyses unless it is properly accounted for

### 2021-07-21 index.Rmd
Update syntax for block environments
Theorem (and similar) environments and custom block environments are
updated to use the new Bookdown syntax based on Pandoc's fenced syntax
for Div blocks; see the Bookdown book for more information. Resolves #7.

>>>>

::: {#preface-warning .rmdnote}

**This in-progress manuscript is not intended for general scientific use.**
It is incomplete, has not been carefully reviewed, and may contain mistakes or other inaccuracies.
Please post comments or questions on the [GitHub Issues page](https://github.com/mikemc/differential-abundance-theory/issues) or [email Mike](m.mclaren42@gmail.com).

:::
